`r title`

### 2018-01-17 lib/report.Rmd
progress

```{r null_rates_table}
null_rates_table
```

@@

Contraband found: `r contraband_found_pct`

```{r plot_props_by_race}
search_conducted_by_race_plot
contraband_found_by_race_plot
```

>>>>

```{r null_rates_tables}
null_rates_table
```

@@

Contraband found (all stops): `r contraband_found_pct`
Contraband found (where search conducted): `r predicated_contraband_found_pct`

```{r plot_props_by_race}
search_conducted_by_race_plot
contraband_found_by_race_plot
predicated_contraband_found_by_race_plot
```
